\section{Violations of the \acrlong{dry} Principle}
The \gls{dry} Principle was formulated in 2000 by Hunt and Thomas.
It states that 
`Every piece of knowledge must have a single, unambiguous, authoritative representation within a system.'\footnote{\cite{pragmaticprogrammer} p. 27}
When we consider the following excerpt we can observe what is most likely a violation of \gls{dry}

\begin{verbatim}
button {
    color: red;
    padding: 5px;
}

a {
    color: red;
    text-decoration: none;
}
\end{verbatim}

Assuming that the intention of the developer was to give both links and buttons an identical color, this piece of knowledge has two authoritative representations here.
But it is possible that the red color may only be identical by coincidence, meaning that it different semantics within the context of either element.
This implies that both definitions will not necessarily be change at the same time.
However, if this is not the case, that repetition may cause additional cost during maintenance.
This is because, if the inherently singular piece of knowledge changes, the code has to be changed in more that one place.
Even automated tools like find and replace are prone to errors of their operators as the operation may require detailed knowledge of the target system.\footnote{cf. \cite{humanautomation} p.408}

There are multiple options to eliminating the problem that has just been examined.
Variables are, to this date, only fully supported by Firefox 31 and has been removed as an experimental feature in Google Chrome from version 33 to 34.\footnote{cf. \cite{cssvariables}}
To eliminate the duplication constants are sufficient.
Besides variables there are no native gls{css} means to emulate constants in their classical definition.

All common \gls{css}-Preprocessors provide a variable feature.
These variables are only variable during the actual processing and not at interpretation-time.
Thus preprocessor variables are effectively constants.\footnote{cf. \cite{wirthpreprocessors} p.27}
Using preprocessors allows eliminating repetition in the source code to some degree
but the repetition will still be observable in the processed \gls{css}.
Verou assumes that the usage of preprocessors may result in the developer `losing track of CSS filesize'.\footnote{cf. \cite{veroupreprocessors}}
This potential may not be as big when using preprocessed variables, but bigger for other language features like mixins.
% information size
% bandwidth for user

An approach to completely eliminate repetition in native \gls{css} code is Atomic \gls{css}, presentend in 2013 by Koblentz, frontend developer at Yahoo.
It advocates splitting the \gls{css} source code in the smallest possible parts.
This effectively decouples the \gls{css} from the structure of the \gls{html} document.
Atomic \gls{css} rules represent a specific visual appearance.
The class names of the individual rules are not semantic but representational.

% approach by frameworks, high reusability

\begin{verbatim}
.Mend-small {
    margin-left: 10px;
}
\end{verbatim}

In contrast to block-based approaches like \gls{suit} and \gls{bem} Atomic CSS is no scoping and no nesting.
Rules do not have a specific context and thus are highly reusable.\footnote{cf. \cite{atomiccssarticle}}
There are multiple tradeoffs to the Atomic CSS approach:

\begin{itemize}
    \item {\normalfont \bfseries Additional classes in markup:} Visual attributes are grouped through class assignment rather than below a specific selector.
        This means more classes need to be assigned to each element whose visual appearence deviates from default and base styles.
        The resulting markup may be considered bloated.

    \item {\normalfont \bfseries Non-semantic class names:} Because of the radical decoupling the \gls{css} rules are named by the visual attribute they yield. 
        The lack of scoping possibly impedes the developer's ability to localize the effect of changes.

    \item {\normalfont \bfseries Changing names and unused rules:} The W3C states that `Good names don't change'.\footnote{\cite{classsemantics}}
        The Usage of class names that inherit attribute values are a violation of \gls{dry}. 
        Replacing these attribute values with names like \verb small may eleminate the need to change class names when the actual attribute values change.
\end{itemize}

The development of the Atomic CSS approach has since been continued by Yahoo.
Current versions do not involve direct editing of \gls{css}-files.
The semantic hierarchy between class names and attributes is inversed.
Class names define the actual style attributes.
Atomizer, a build tool that extracts \gls{css} rules from the definitions in the markup is used to generate gls{css}-files.
Atomizer supports the usage of variables.
Whereas an overhead of unused rules in the \gls{css}-files is prevented by this approach, the markup is still studded with non-semantically named classes.\footnote{cf. \cite{atomiccsssite}}

% vs inline styles
% applying and de-applying classes, meaning of classes, logic has to be stored in module context
Hower
effectively a preprocessor
Atomic Design by ??? 

Modules / Components
modifiers on components or elements
balance between repeating 





no variables
repeated within the markup

respect to SOLID design principles\footnote{cf. \cite{solidcss}}
sub-classes = re-usability through dry
cascade

DRY Principle \footnote{cf. \cite{pragmaticprogrammer}}
low reusability
- specificity
- tight coupling with markup

DRY CSS: breaks code structure
